On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 qpip.tex
Make editorial changes

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	Let $\varepsilon=T^{-c}$. \Ethan{Try setting up this $\varepsilon$ more intuitively}
	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
	Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
	Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item $c\gets0$
		\item $y\gets\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then set $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}

\begin{theorem}
    \label{QPIP1thm}
	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness and soundness $(O(T^{-c}), O(T^{-c}))$ for any constant $c$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.

>>>>

\begin{protocol}{$\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoQPIP1}
	Take $\varepsilon>0$
	Let $m$ be large enough so that $\frac{1}{2^m}$ is negligible in $\varepsilon$
	Let $n$ be large enough so both $P\left[Bin(n, \frac{1}{2}-2\varepsilon)\geq\left(\frac{1}{2}-\varepsilon\right)n\right]$ and $P\left[Bin(n, \frac{1}{2})\leq\left(\frac{1}{2}-\varepsilon\right)n\right]$ are negligible in $\varepsilon$ by Chernoff bound
	Let $N$ be large enough so that $\sqrt{\frac{2(m+n)^2\ln\abs{A}}{N-(m+n)}}<\varepsilon$, where $\abs{A}$ is the number of qubits in $\ket{\psi_{C(x)}}$.
	\begin{enumerate}
		\item The honest prover sends $N$ identical copies of $\ket{\psi_{C'(x)}}$, where $C'$ is $C$ padded with identities as mentioned in \hyperref[idpadding]{Observation~\ref*{idpadding}}
		\item The verifier randomly picks $m$ copies for outputting and $n$ copies for checking
		\item Set up a counter $c=0$
		\item Set $y=\bot$
		\item For $i$ from $1$ to $N$:
		\begin{enumerate}
			\item If the $i$-th register is for checking:
			\begin{enumerate}
				\item The verifier runs \autoref{AlgGroundStateCheck} as described by \hyperref[ProtoGroundStateCheck]{Observation~\ref*{ProtoGroundStateCheck}}.
				\item If the test passes, increment counter $c$.
			\end{enumerate}
			\item If the register is for outputting:
			\begin{enumerate}
				\item The verifier measures the copy in standard basis
				\item If the measurement result of the clock register $\geq\frac{T}{2}$ and $y=\bot$, then update $y$ as the measurement result of the data register.
			\end{enumerate}
			\item Otherwise, just measure the entire register in standard basis and discard it.
		\end{enumerate}
		\item If $\frac{c}{n}\geq\frac{1}{2}-\varepsilon$:
		\begin{enumerate}
			\item If $y\ne\bot$ then output $y$
			\item Otherwise, reject.
		\end{enumerate}
		\item Otherwise, reject.
	\end{enumerate}
\end{protocol}

\begin{theorem}
    \label{QPIP1thm}
	For any $L\in\SampBQP$, \hyperref[ProtoQPIP1]{Protocol~\ref*{ProtoQPIP1}} is a protocol for $L$ with negligible completeness. $\forall c\in\bbN$, it achieves soundness $(\varepsilon, \varepsilon)$ where $\varepsilon=T^{-c}$. Furthermore, in this protocol, the verifier doesn't need to apply any gates, and only needs to apply $X$ and $Z$ measurements.
\end{theorem}
\begin{proof}
	It clearly has completeness negligibly close to $1$. Now we analyze soundness against a possibly cheating prover that has at least $\delta$ probability to be accepted. Let $\sigma$ be the state the prover sends to the verifier.
